Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-10-31 Latex_files/Thesis/chapters/chapter 3/main.tex
chapter 3 updates

If multiple micro-rotors could be trapped in close proximity 
to one another they could create a large region of fluid where 
nucleation is more likely than the bulk fluid. Because optical
torque is not contingent on the fluid properties the only 
limiting factor would be the total angular momentum transferred 
to each particle. Micro-rotors have been created that allow for 
precise control of suspended micro-particles \cite{Butaite2019} 
and could potentially be used to generate sufficient shearing. 
However these could not be used in this project as we lacked the 
necessary hardware to form multiple gradient traps.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nucleation with a Stationary and Moving Beam}
As mentioned previously, shearing via optical rotation did 
not result in any localised nucleation events even while 
in the proximity of the droplet edge. An alternative approach
was suggested, using a galvano mirror to move a particle 
quickly through a supersaturated solution. While a particle
is within the optical trap the gradient forces are 
significantly reduced meaning simply trapping a particle is
insufficient for inducing nucleation \cite{Flannigan2023}. 
This is why we did not see any nucleation events while 
rotating the vaterite, there is not a large gradient force
to draw in material. We did not consider a focus beam by 
itself as this has already been demonstrated in previous
experiments \cite{Flannigan2023, Liao2022, Rungsimanon2010}.

Preliminary calculations suggested a particle moving rapidly
through a fluid could produce significantly greater shear 
rates (see \emph{Appendix X.X} for breakdown) than a rotating 
particle. During initial testing using silica beads we found 
that even in undersaturated solutions the optical trap would 
produce a crystal nucleus when the trap was empty. This has 
been reported prior \cite{Rungsimanon2010, Liao2022}, but 
what is more interesting is how the beam's motion influenced 
the growth of the nucleus.

\subsection{Stationary beam}
\label{sec:stationary}
Its well known that a supersaturated solution can nucleate
if irradiated by a focused beam. We confirmed that our 
laser was of sufficient power and focus to induce crystal
nucleation. The laser was focused at the edge of a $20\mu L$
droplet consisting of water and dissolved glycine ($S=1.03$). 
The solution was monitored for 10 minutes, if a nucleation 
event was observed the event was recorded using a high speed 
CCD. If no nucleation event was observed after 10 minutes 
the solution was disposed of and a new sample was prepared. 
After ten repeats only 30\% of the samples observed a 
nucleation event at the focus. All of which displayed similar 
behaviour to one another.

Consider Fig.~\ref{fig:stationary_beam}, the frames taken from 
a nucleation event, the beam is a stationary being $\approx3.5 
\mu m$ from the droplet edge. After a period of roughly 5 minutes 
a nucleus forms at the trap focus, growing quickly (growth rate 
was approximated using imageJ to be on the order of $700\ \mu 
m^2/min$) from the focal point of the trap until after roughly 
$6$ seconds the crystal escapes. Comparing to previous literature
using optical tweezers shows that the growth rate is only loosely 
connected to the solutions supersaturation. Crystal growth rates 
for a solution of glycine and water ($S\approx1.00$) was found to
vary from as much as $3900 \mu\ m^2/min$ to as low as $675\mu 
m^2/min$. Local conditions play a much larger role in the growth 
rate than just the concentration \cite{Flannigan2023}. A likely 
reason that the trap is escaped is due to the fact that crystal 
is far too large to be held in place and is in fact still growing 
as the solution is supersaturated. The key take away to remember 
is that the beam has no influence over the crystal shape, instead 
it grows outward from the trap focus. Furthermore, due to the fact 
that the solution is supersaturated the crystal growth cannot be 
contained to the trap focus. Instead the crystal escapes as its 
size exceeds the trap focus. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.75\linewidth, height=1.1\linewidth]{frames_no_beam_movement.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of supersaturated 
	glycine solution. (b) shows the first instance of a crystal nucleus, growing 
	quickly through (c)-(e) until after $6.665\ s$ the crystal begins to escape 
	the trap.}
	\label{fig:stationary_beam}
\end{figure}

\newpage
\subsection{Moving Beam}
\label{sec:moving}
To test if a rapidly moving silica bead could generate the necessary shear rate 
for crystal nucleation we wanted to see if a trapped silica bead could be trapped
and moved in an aqueous solution. $20\ \mu L$ of glycine and water ($S=1.03$) was 
added to $10\ \mu L$ of a dilute water-silica mixture making the solution 
unsaturated ($S\approx0.7$). However, due to the beam's motion we instead 
encountered several unexpected results.

Shown below in Fig.~\ref{fig:eliptical_beam_1} where we have the laser focus 
moving in a small elliptical pattern; interestingly. After a few minutes we 
noted the appearance of several small droplets (see figure~\ref{fig:cluster_trapping}
for a larger example of these droplets). These appear too have a wide distribution
of sizes, unlike silica microspheres which have a uniform radius of $1.57\ 
\mu m$. We surmise these could be small clusters of Glycine that had previously 
been shown to form when the aqueous solutions where irradiated with a 
focused laser \cite{Tsuboi2009, Gowayed2021}. While no droplets are seen 
directly entering the focus a nucleus forms close to the droplet edge, 
unlike in Fig.~\ref{fig:stationary_beam} the crystal does not grow out from 
the focal point evenly. Due to the galvano mirror, the crystal is simultaneously 
being moved by and growing around the focal point of the trap. Because of 
this the crystal nucleus lacks a clear morphology at first. Until roughly 
$20\ s$ the crystal reaches a almost prismatic structure, with further 
irradiation increasing the size.

Interestingly the galvano-mirror allows the trap to impart a slight torque 
on the crystal, as shown in fig.~\ref{fig:eliptical_beam_1}(c) and (d), 
where even though the crystal is not directly in the trap focus it rotates 
in the $x-y$ plane and gets trapped again at a corner. The rotation could 
not be due to fluid flow close to the surface of the crystal as the dipole 
moment of individual water molecules is too small to be influenced by an 
optical trap. In figs.\ref{fig:eliptical_beam_1}(e) and (f), the crystal 
growth becomes localised to the corner. The area growth rate between figures \ref{fig:eliptical_beam_1}(a) and (d) was approximated using imageJ at $45.03\ 
\mu m^2 /min$, where as between figures \ref{fig:eliptical_beam_1}(e) and 
(f) the growth rate at that particular edge was estimated at $42.10\ \mu m^2/min$. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.85\linewidth]{frames_eliptical_beam.pdf}
	\caption{Frames from a longer video depicting the growth 
		of a nucleus using a moving beam. Beam power is kept 
		at 700 mW and the supersaturation was estimated at 
		S=0.86. Initially the crystal shape is amorphous (a) 
		but eventually reaches a more regular shape (b). This crystal is still influenced by the optical trap as 
		even when not directly irradiated by the laser the 
		crystal rotates between (c) and (d). When the laser 
		is focused on a corner the crystal growth is localised 
		to that region, resulting in an elongated section 
		forming between frames (e) and (f).}
	\label{fig:eliptical_beam_1}
\end{figure}

Nucleation in undersaturated conditions has been reported previously in $D_2O$ 
\cite{Rungsimanon2010} and $H_2O$ \cite{Flannigan2023}, though not involving a 
moving beam. This modification allows for the crystal growth to be localised to
a specific region of the bulk crystal whereas with a stationary beam there is no
control over the crystal morphology. In fact this allows for a much finer control
over the exact shape of the crystal nucleus, in some cases allowing for growth out
of the viewing plane as shown in

\begin{figure}
	\centering
\end{figure}

\subsection{Direct trapping of Glycine clusters}
\label{sec:clusters}
One common aspect involving these droplets is the fact when brought 
to the laser focus the droplets would nucleate immediately 
\cite{Liao2022}. A solution similar to Sec~\ref{sec:stationary} was 
made up, but without any silica droplets. Once again the beam was 
focused close to the droplet edge, this time the galvano mirror was 
scanning a circular path (as shown in figure~\ref{fig:cluster_trapping}). 
After a few minutes of irradiation droplets were seen entering the 
camera frame, because no silica had been added these droplets had 
to be from the glycine solution. Trapping individual droplets did 
not result in immediate nucleation even after several minutes being 
trapped. Trying to bring two droplets together resulted in nucleation 
between the two droplets, compared to \ref{sec:stationary} \& 
\ref{sec:moving} the growth is much slower, taking nearly 40 seconds 
before the crystal structure becomes clearer.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\linewidth]{cluster_trapping.pdf}
	\caption{Frames from a longer video demonstrating the trapping of a glycine 
		droplet. Solution is undersaturated glycine and water (S = 0.86), with the 
		laser power is set at $750\ mW$. (a) shows a trapped droplet (outlined in 
		black) being brought into contact with a larger droplet. (b) upon contact 
		a nucleus can be seen between the two droplets. The growth is rather slow 
		with the crystal having no clear defined morphology through (c) and (d). 
		Between frames (e) and (f) the larger droplet finally joins the main crystal.}
	\label{fig:cluster_trapping}
\end{figure}

The fact that these droplets can be trapped indicates they must 
have a higher refractive index than the surrounding solution. 
Previous reports have shown that a focused trap will draw in 
solute material from the bulk \cite{Tsuboi2009, Gowayed2021}. It 
has been shown that the concentration of glycine solution is correlated 
with the refractive indices of the liquid \cite{Gowayed2021, Orttung1963}. 
This suggests that these droplets serve to provide solute material 
to the bulk crystal.

\newpage

\subsection{Influence of a moving beam front on seed crystals}
One potential application of this phenomena would be in using a 
moving the moving beam front as a method for shaping the final
crystal morphology. Glycine seed crystals were grown via 
evaporative crystallisation over night. The resultant crystals
were as wide as $0.5 mm$ in some cases. Individual crystals were 
collected and suspended in a water + glycine solution ($S = 1.001$)
and the laser was scanned along a narrow linear path.

As shown by fig.~\ref{fig:seed_crystals} the laser does not in fact 
promote crystal growth but instead forces the crystal to dissolve 
into the bulk solution. The dissolution rate is not as substantial 
as the growth rate seen in previous sections. It takes over 20 
minutes for the for the crystal surface to dissolve more than a 
few microns. Furthermore we do not report any sightings of droplets
close to the surface of the crystal nor do we see anything enter the 
optical trap.
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{seed_crystals.pdf}
	\label{fig:seed_crystals}
	\caption{Frames from a seed crystal being irradiated by a scanning
		laser. The laser path is shown below in red. Initially the 
		crystal edge is nearly perpendicular to the laser path. However,
		over the course of nearly twenty minutes the crystal around the 
		laser has dissolved leaving a concave indent.}
\end{figure}

@@

\section{Summary of Moving Beam Phenomena}
To summarise, the introduction of a moving beam helps to accelerate the 
local growth of a newly formed crystal. This is due to the presence of 
glycine droplets that accumulate near the interface between the liquid 
solution and air. The theory behind the localised growth can be summarised 
thusly.

Initial nucleation is similar to typical optical trapping induced nucleation,
with the air solution interface limiting the molecular mobility of the solute
molecules \cite{Liao2022, Sugiyama2009, Gowayed2021}. The moving beam front 
can influence the motion of the nucleus initially, but eventually the drag 
force means the crystal is not moved by the optical trap. Localised crystal
growth occurs when the trap is close to or partially over the interface of 
the crystal (see figure~\ref{fig:local_nucleation}(a)). As shown in \ref{sec:clusters}, 
the optical trap can manipulate these droplets similar 
to microspheres. When in close proximity to the trap these droplets are 
brought towards the crystal surface (see figure~\ref{fig:local_nucleation}(b)). 
These provide material that grows the crystal around that region (see figure~\ref{fig:local_nucleation}(c)). Eventually the local solution is either 
depleted of solute material or the crystal front has grown to fully encompass 
the trap, preventing further growth (see figure~\ref{fig:local_nucleation}(d)). 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\linewidth]{galvano_diagram.pdf}
	\caption{Diagram outlining how a moving beam assists in the growth of a crystal
		nucleus. (a) a crystal nucleus is partially trapped by a moving beam with 
		solute droplets close to its surface. (b) droplets close to the laser
		focus are drawn in by gradient forces and moved towards the crystal surface.
		(c) these droplets provide material to the main crystal, resulting in
		localised growth around the laser focus. (d) eventually the crystal area 
		either fully surrounds the laser focus or the solution surrounding the laser
		is depleted of solute material.}
	\label{fig:local_nucleation}
\end{figure}

The reason the seed crystals saw no further crystal growth when irradiated 
with the trap is due to the fact that these experiments were carried out 
in a bulk solution, absent of any interfaces. As such the clusters seen in
\ref{sec:moving} \& \ref{sec:clusters} are not present and cannot provide
material to accelerate crystal growth.

There are still several factors that need to be investigated, but due to time
constraints it was not possible to properly study this phenomena. Firstly, 
there is the question of what conditions result in the production of concentrated
droplets, it is not clear if the presence of a laser is required or if these
droplets naturally occurring. Prior literature would suggest that the laser is 
required \cite{Liao2022, Tsuboi2009}, but this would not explain why in many 
cases the droplets are found far outside the influence of the optical trap. It
has been suggested that optical traps can attract microspheres over a wider 
area, but it is hard to say that this would result in the creation of liquid 
droplets \cite{Yi2021}.

@@

\section{Conclusion}

In conclusion, the experimental results from this chapter provide no 
affirmative evidence of shear induced crystal nucleation. This is in
part due to the limited rotational speed that could be achieved using
vaterite microspheres. Simply adding a micro-rotor to a supersaturated
solution will not yield a significant fluid flow to induce crystal 
nucleation. Furthermore, the region in which the local shear rate is 
significant enough is so small that any nucleation events that could 
occur there would not grow large enough to be stable. This does not 
however, suggest that shear induced nucleation is impossible at a 
micro scale. In fact there have been several developments lately that
allow for the precise rotation of multiple rotors to control the 
precise motion of silica beads. The challenge lies in both building the
optical equipment to form multiple strong traps (~ 3 per rotor). These 
traps would have to be strong enough to not only hold the rotors but 
also move them at a sufficiently fast rotational speed that they could
induce a significant enough fluid flow.

On the other hand, the results utilising the galvano mirror have some 
interesting implications for future research into crystal nucleation
using optical tweezers. We noted that in undersaturated conditions the
presence of 'droplets' that could be trapped and later nucleated when 
brought into contact with one another. The fact that these droplets 
could be trapped suggests they have a higher refractive index to the 
solution, given that the solutions were filtered prior to irradiation
dismisses that they could be dust particles. Prior literature suggests
that optical trapping of a supersaturated solution can lead to the 
production of nano droplets \cite{Gowayed2021, Tsuboi2009}. Controlling
the localised growth requires that the growth and trapping are handled
by two separate lasers. Optical traps for amorphous solids has been 
shown as a possibility but the algorithm would need to be adaptive 
to the changing crystal shape.

>>>>

If multiple micro-rotors could be trapped in close proximity 
to one another they could create a large region of fluid where 
nucleation is more likely than the bulk fluid. Because optical
torque is not contingent on the fluid properties the only 
limiting factor would be the total angular momentum transferred 
to each particle. Micro-rotors have been created that allow for 
precise control of suspended micro-particles \cite{Butaite2019} 
and could potentially be used to generate sufficient shearing. 
However these could not be used in this project as we lacked the 
necessary hardware to form multiple gradient traps.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nucleation with a Stationary and Moving Beam}
As mentioned previously, shearing via optical rotation did 
not result in any localised nucleation events even while 
in the proximity of the droplet edge. An alternative approach
was suggested, using a galvano mirror to move a particle 
quickly through a supersaturated solution. Preliminary 
calculations suggested a particle moving rapidly through 
a fluid could produce significantly greater shear rates 
(see \emph{Appendix X.X} for breakdown) than a rotating 
particle. While a particle is within the optical trap the 
gradient forces are significantly reduced meaning simply 
trapping a particle is insufficient for inducing nucleation \cite{Flannigan2023}. This is why we did not see any 
nucleation events while rotating the vaterite, there is 
not a large gradient force to draw in material.

During initial testing using silica beads we found that 
even in undersaturated solutions the optical trap would 
produce a crystal nucleus when the trap was empty. This 
has been reported prior \cite{Rungsimanon2010, Liao2022}, 
but what is more interesting is how the beam's motion 
influenced the growth of the nucleus.

\subsubsection{Choice of Crystal growth rate units}
The growth rate of a crystal can be described using different
units depending on the situation. For example, seed crystals 
often use growth units in the form of \textit{length per unit
time}. This can either be used to describe the overall length
of the longest edge of a crystal, or to describe how individual
faces grow separately. This works well for crystals with a 
clear morphology, in regards to laser induced nucleation the 
crystal growth is heavily influenced by the local fluid 
conditions meaning tracking the length of an individual face 
is challenging. Instead we utilise image analysis software 
such as imageJ to measure the area of the crystal after each 
frame to get a rough estimate of the crystal growth rate in 
units of \textit{length$^2$ per unit time}. With the addition 
of the contact angle information from \cite{Flannigan2023} we 
can approximate the crystal height based on how close it is to 
the droplet edge.

\subsection{Stationary beam}
\label{sec:stationary}
Its well known that a supersaturated solution can nucleate
if irradiated by a focused beam with sufficient power 
\cite{Rungsimanon2010}. First we look at how a laser induced
nucleation event unfolds using a stationary focused beam. 
The laser was focused at the edge of a $20\mu L$ droplet 
consisting of water and dissolved glycine ($S=1.03$). The 
solution was monitored for 10 minutes, if a nucleation event 
was observed the event was recorded using a high speed CCD. 
If no nucleation event was observed after 10 minutes the 
solution was disposed of and a new sample was prepared. After 
ten repeats only 30\% of the samples observed a nucleation 
event at the focus. All of which displayed similar growth 
behaviour to one another.

Consider Fig.~\ref{fig:stationary_beam}, the frames taken from 
a nucleation event, the beam is a stationary being $\approx3.5 
\mu m$ from the droplet edge. After a period of roughly 5 minutes 
a nucleus forms at the trap focus, growing quickly (growth rate 
was approximated using imageJ to be on the order of $700\ \mu 
m^2/min$) from the focal point of the trap until after roughly 
$6$ seconds the crystal escapes. A likely reason that the trap 
is escaped is due to the fact that crystal is far too large to 
be held in place and is in fact still growing as the solution is supersaturated. Based on the contact angle measurements from \cite{Flannigan2023}, the droplet height could not have been 
any more than $2-5\mu m$ at the trap focus.
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth, height=1.3\linewidth]{frames_no_beam_movement.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of supersaturated 
	glycine solution. (b) shows the first instance of a crystal nucleus, growing 
	quickly through (c)-(e) until after $6.665\ s$ the crystal begins to escape 
	the trap.}
	\label{fig:stationary_beam}
\end{figure}

Comparing to previous literature using optical tweezers shows 
that the growth rate is only loosely connected to the solutions 
supersaturation. Crystal growth rates for a solution of glycine 
and water ($S\approx1.00$) was found to vary from as much as 
$3900 \mu\ m^2/min$ to as low as $675\mu m^2/min$ 
\cite{Flannigan2023}. The reason for such high crystal growth 
rates is due primarily to the tweezer focus bringing in material 
due to gradient forces. A study of glycine crystals in water 
found that for a similarly supersaturated solution the growth 
rate along the {011} face was around $0.1\ \mu m/min$ where as 
the {010} face was found to have a growth rate of around $0.01\ 
\mu m/min$. While its difficult to extrapolate an exact area 
growth rate from these results we can approximate that if the 
we looked directly perpendicular to the crystal growth the area 
would increase at $\approx0.02\ \mu^2/min$ (see X.X for a 
breakdown of this approximation).

The key take away to remember is that the beam has no influence 
over the crystal shape, instead it grows outward from the trap 
focus. Furthermore, due to the fact that the solution is 
supersaturated the crystal growth cannot be contained to the 
trap focus. Instead the crystal escapes as its size exceeds the 
trap focus.

\subsection{Moving Beam}
\label{sec:moving}
To test if a rapidly moving silica bead could generate the 
necessary shear rate for crystal nucleation we wanted to 
see if a trapped silica bead could be trapped and moved in 
an aqueous solution. $20\ \mu L$ of glycine and water ($S=
1.03$) was added to $10\ \mu L$ of a dilute water-silica 
mixture making the solution unsaturated ($S\approx0.7$). 
However, due to the beam's motion we instead encountered 
unexpected growth behaviour.

Shown below in Fig.~\ref{fig:eliptical_beam_1} where 
we have the laser focus moving in a small elliptical 
pattern. While nothing is seen directly entering the 
focus a nucleus forms close to the droplet edge, 
unlike in fig.~\ref{fig:stationary_beam} the crystal 
does not grow out from the focal point evenly. Due to 
the galvano mirror, the crystal is simultaneously 
being moved by and growing around the focal point of 
the trap. Because of this the crystal nucleus lacks 
a clear morphology at first. Until roughly $20\ s$ 
the crystal reaches a almost prismatic structure, 
with further irradiation increasing the size.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\linewidth]{frames_eliptical_beam.pdf}
	\caption{Frames from a longer video depicting the growth 
		of a nucleus using a moving beam. Beam power is kept 
		at 700 mW and the supersaturation was estimated at 
		S=0.86. Initially the crystal shape is amorphous (a) 
		but eventually reaches a more regular shape (b). This crystal is still influenced by the optical trap as 
		even when not directly irradiated by the laser the 
		crystal rotates between (c) and (d). When the laser 
		is focused on a corner the crystal growth is localised 
		to that region, resulting in an elongated section 
		forming between frames (e) and (f).}
	\label{fig:eliptical_beam_1}
\end{figure}

Interestingly the galvano-mirror allows the trap to 
impart a slight torque on the crystal, as shown in fig.~\ref{fig:eliptical_beam_1}(c) and (d), where even 
though the crystal is not directly in the trap focus 
it rotates in the $x-y$ plane and gets trapped again 
at a corner. The rotation could not be due to fluid 
flow close to the surface of the crystal as the 
dipole moment of individual water molecules is too 
small to be influenced by an optical trap. In figs.\ref{fig:eliptical_beam_1}(e) and (f), the 
crystal growth becomes localised to the corner. The 
area growth rate between figures \ref{fig:eliptical_beam_1}
(a) and (d) was approximated using imageJ at $45.03\ 
\mu m^2 /min$, where as between figures 
\ref{fig:eliptical_beam_1}(e) and (f) the growth rate 
at that particular edge was estimated at $42.10\ \mu m^2/min$.

Nucleation in undersaturated conditions has been 
reported previously in $D_2O$ \cite{Rungsimanon2010} 
and $H_2O$ \cite{Flannigan2023}, though not involving 
a moving beam. This modification allows for the crystal 
growth to be localised to a specific region of the bulk 
crystal whereas with a stationary beam there is no 
control over the crystal morphology. In fact this allows 
for a much finer control over the exact shape of the 
crystal nucleus, in some cases allowing for growth out
of the viewing plane as shown in fig.~\ref{fig:out_of_plane}.
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{out_of_plane.pdf}
	\caption{Interesting crystal growth on the surface of an
	existing crystal. Initially the crystal surface seems 
	flat (a) but eventually a different crystal structure 
	grows out off of the surface (b).}
	\label{fig:out_of_plane}
\end{figure}

Where a large outgrowth forms on the surface of a nucleus,
over a period of $30\ s$ the outgrowth develops into a 
rhombic crystal structure. The unique crystal growth 
demonstrated is likely a factor of the moving beam focus,
but this raises a question over how the laser can localise
the growth only around the focus and why the crystal does 
not grow or shrink when not directly within the trap. There
should be some material that is being drawn into the trap
as it scans across the camera frame.

\subsection{Direct trapping of Glycine clusters}
\label{sec:clusters}
In a repeat experiment a solution similar to sec.~
\ref{sec:stationary} was made up, but without any 
silica micro-spheres. Once again the beam was focused 
close to the droplet edge, this time the galvano 
mirror was scanning a circular path (as shown in fig.~\ref{fig:cluster_trapping}). After a few 
minutes of irradiation droplets were seen entering 
the camera frame. Because no silica had been added, 
and that the solutions were filtered, these droplets 
had to be from the glycine solution. Trapping 
individual droplets did not result in immediate 
nucleation even after several minutes being trapped. 
Trying to bring two droplets together resulted in 
nucleation between the two droplets, compared to 
\ref{sec:stationary} \& \ref{sec:moving} the growth 
is much slower, taking nearly 40 seconds before the 
crystal structure becomes clearer.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\linewidth]{cluster_trapping.pdf}
	\caption{Frames from a longer video demonstrating the trapping 
		of a glycine droplet. Solution is undersaturated glycine 
		and water (S = 0.86), with the laser power is set at $750\ 
		mW$. (a) shows a trapped droplet (outlined in black) being 
		brought into contact with a larger droplet. (b) upon contact 
		a nucleus can be seen between the two droplets. The growth 
		is rather slow with the crystal having no clear defined 
		morphology through (c) and (d). Between frames (e) and (f) 
		the larger droplet finally joins the main crystal.}
	\label{fig:cluster_trapping}
\end{figure}

The fact that these droplets can be trapped indicates 
they must have a higher refractive index than the 
surrounding solution. Previous reports have shown that 
a focused trap will draw in solute material from the 
bulk \cite{Tsuboi2009, Gowayed2021}. This suggests that 
the droplets observed are concentrated spheres of glycine, 
which also explains how nucleation was initiated when those
two spheres were brought into contact with one another. The 
droplets must be providing material for the crystal growth.
It has been shown that the concentration of glycine solution 
is correlated with the refractive indices of the liquid 
\cite{Gowayed2021, Orttung1963}. This suggests that we could
measure the concentration of individual droplets based on the
trapping strength of each droplet. 
\newpage

\subsection{Influence of a moving beam front on seed crystals}
\label{sec:seed_crystals}
One potential application of this phenomena would be in using 
a moving the moving beam front as a method for shaping the 
final crystal morphology. Therefore, we wanted to test if a 
moving beam front could have any influence on the shape of a
seed crystal submerged in a bulk solution. Glycine seed crystals 
were grown via evaporative crystallisation over night. The 
resultant crystals were as wide as $0.5 mm$ in some cases. 
Individual crystals were collected and suspended in a water 
+ glycine solution ($S = 1.001$) and the laser was scanned 
along a narrow linear path. It should be noted that the seed 
crystal was fully submerged in the solution, meaning that there
is no interface between the air and solution close to the seed.
Five separate repeats were conducted, all demonstrating similar
behaviour to one another.

As shown by fig.~\ref{fig:seed_crystals} the laser does not 
in fact promote crystal growth but instead forces the crystal 
to dissolve into the bulk solution. The dissolution rate is not 
as substantial as the growth rate seen in previous sections. 
It takes over 20 minutes for the for the crystal surface to 
dissolve more than a few microns. Furthermore we do not report 
any sightings of droplets close to the surface of the crystal 
nor do we see anything enter the optical trap.
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{seed_crystals.pdf}
	\caption{Frames from a seed crystal being irradiated by a 
		scanning laser. The laser path is shown below in red. 
		Initially the crystal edge is nearly perpendicular to 
		the laser path. Over the course of nearly twenty minutes 
		the crystal around the laser has dissolved leaving a 
		concave indent.}
	\label{fig:seed_crystals}
\end{figure}

@@

\section{Summary of Moving Beam Phenomena}
To summarise, the introduction of a moving beam helps to 
accelerate the local growth of a newly formed crystal. It 
seems that this phenomena will only occur when close to 
interface between the solution and air. We note the presence
of droplets that can sometimes be seen entering the trap, 
though this is not always necessary for a nucleation event 
to occur. A plausible description of the phenomena is described
thusly.

Initial nucleation is similar to typical optical trapping 
induced nucleation, with the air solution interface limiting 
the molecular mobility of the solute molecules \cite{Liao2022, 
Sugiyama2009, Gowayed2021}. The moving beam front can influence 
the motion of the nucleus initially, but eventually the drag 
force means the crystal is not moved by the optical trap. 
Localised crystal growth occurs when the trap is close to or 
partially over the interface of the crystal (see fig.~
\ref{fig:local_nucleation}(a)). This suggests that the 
laser itself is bringing in new solute material that can then
adhere to the crystal surface. Interestingly even when the 
crystal growth is localised to a small section of the crystal
we do not observe the crystal dissolving. This is consistent 
with other observed laser induced nucleation results, where 
as long as the laser is active the crystal remains stable 
within the solution \cite{Flannigan2023, Rungsimanon2010,
Liao2022, Sugiyama2009}. It does raise further questions 
however, mainly in an undersaturated solution is a moving 
beam front able to increase the size of the formed nucleus
compared to a stationary beam? Additionally, it raises the 
question about what the role the 'glycine droplets' play in 
the nucleation process.

As shown in \ref{sec:clusters}, the optical trap can manipulate 
these droplets similar to microspheres. When in close proximity 
to the trap these droplets are brought towards the crystal 
surface (see fig.~\ref{fig:local_nucleation}(b)). We have 
already suggested that these droplets must contain glycine as 
they are to large to be a silica microsphere, and the solutions 
were filtered prior to being studied. The droplets provide 
material that grows the crystal around that region (see fig.~\ref{fig:local_nucleation}(c)). Eventually the local 
solution is either depleted of solute material or the crystal 
front has grown to fully encompass the trap, preventing further 
growth (see fig.~\ref{fig:local_nucleation}(d)). 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\linewidth]{galvano_diagram.pdf}
	\caption{Diagram outlining how a moving beam assists in the 
		growth of a crystal nucleus. (a) a crystal nucleus is 
		partially trapped by a moving beam with solute droplets 
		close to its surface. (b) droplets close to the laser
		focus can be drawn in by gradient forces and moved 
		towards the crystal surface. (c) the laser brings in 
		material that is then deposited on the surface of the 
		crystal. (d) eventually the crystal area either fully 
		surrounds the laser focus or the solution surrounding 
		the laser is depleted of solute material.}
	\label{fig:local_nucleation}
\end{figure}

What remains unclear is why the solution interface is necessary
for localised crystal growth. We know that the glycine droplets 
will form when the laser is close to the glass-solution interface
\cite{Gowayed2021, Yuyama2010, Yuyama2012}. This is consistent 
with our results as being able to image the droplet edge requires 
that the laser is brought close to the cover slip. However it is 
not clear how exactly these droplets contribute to localised 
crystal growth as in sec.~\ref{sec:moving} no droplets are seen 
entering the trap. It seems likely that the presence of droplets 
is necessary as we see that the seed crystals dissolve while 
there are no droplets present.

There are still several factors that need to be investigated. 
Firstly, there is the question of what conditions result in the 
production of concentrated droplets, it is not clear if the 
presence of a laser is required or if these droplets naturally 
occurring. Prior literature would suggest that the laser is 
required \cite{Liao2022, Tsuboi2009}, but this would not explain 
why in many cases the droplets are found far outside the influence 
of the optical trap. It has been shown that phase separation 
occurs when a trap is focused close to the cover slip 
\cite{Gowayed2021, Yuyama2010, Yuyama2012}, but there has been 
no cases of nucleation occurring at the cover slip. Furthermore
these experiments all occurred in supersaturated condition 
($S\ge 1.50$) with a much wider focus ($NA \le 1.00$) whereas 
our results occurred in undersaturated conditions with a 
tighter focus. We did not not any occurrence of a phase 
separation as reported by \cite{Gowayed2021, Yuyama2010, Yuyama2012}
and yet we see the appearance of droplets that we surmise 
are partially constructed of glycine.

@@

\section{Conclusion}
In conclusion, the experimental results from this chapter 
provide no affirmative evidence of shear induced crystal 
nucleation. This is in part due to the limited rotational 
speed that could be achieved using vaterite microspheres. 
Simply adding a micro-rotor to a supersaturated solution 
will not yield a significant fluid flow to induce crystal 
nucleation. Furthermore, the region in which the local 
shear rate is significant enough is so small that any 
nucleation events that could occur there may not grow large 
enough to be stable. This does not however, suggest that 
shear induced nucleation is impossible at a micro scale. 
In fact there have been several developments lately that
allow for the precise rotation of multiple rotors to 
control the precise motion of silica beads \cite{Butaite2019}. 
This would allow for direct control of the shear rate 
within a given volume of fluid, allowing one to study the 
impact of fluid flow on a nucleus at a micro-scale.

On the other hand, the results utilising the galvano mirror 
have some interesting implications for future research into 
crystal nucleation using optical tweezers. We noted that a 
moving beam front is capable of localising the crystal growth
around the beam focus in undersaturated conditions. Typically
in laser induced nucleation the final crystal morphology is 
influenced primarily by the local fluid conditions 
\cite{Flannigan2023, Liao2022}. If this phenomena could be 
fully understood we could have a means of directly manipulating 
the morphology of any nucleating crystal. We noted that in 
undersaturated conditions the presence of droplets that could 
be trapped and later nucleated when brought into contact with 
one another. There remains some uncertainty over the role these 
droplets play in a nucleation event. Further research is also 
necessary to understand how the fluid and laser parameters 
(i.e. supersaturation and numerical aperture) impact the 
formation of these droplets. The fact that these droplets could 
be trapped suggests they have a higher refractive index to the 
solution, given that the solutions were filtered prior to 
irradiation dismisses that they could be dust particles. Prior 
literature suggests that optical trapping of a supersaturated 
solution can lead to the production of nano droplets 
\cite{Gowayed2021, Tsuboi2009}.
